04_DESeq_sexes

### 2019-07-20 analysis/04_DESeq2_sexes.Rmd
now with two parts manipulation

>>>>

```{r offspringremoval}
g <- plotremoval(DEGs.female_hypothalamus, "Female hypothalamus", "bottom")
h <- plotremoval(DEGs.female_pituitary, "Female pituitary", "none")
i <- plotremoval(DEGs.female_gonad, "Female gonad",  "none")
j <- plotremoval(DEGs.male_hypothalamus, "Male hypothalamus", "none")
k <- plotremoval(DEGs.male_pituitary, "Male pituitary", "none")
l <- plotremoval(DEGs.male_gondad, "Male gonad", "none")

pdf("../figures/sexes/offspringremoval-1.pdf", width = 10, height = 6)
plot(mybarplots2)
dev.off()

```{r prolongextend}
g <- plotprolongdelay(DEGs.female_hypothalamus, "Female hypothalamus", "bottom")
h <- plotprolongdelay(DEGs.female_pituitary, "Female pituitary", "none")
i <- plotprolongdelay(DEGs.female_gonad, "Female gonad",  "none")
j <- plotprolongdelay(DEGs.male_hypothalamus, "Male hypothalamus", "none")
k <- plotprolongdelay(DEGs.male_pituitary, "Male pituitary", "none")
l <- plotprolongdelay(DEGs.male_gondad, "Male gonad", "none")

pdf("../figures/sexes/prolongextend-1.pdf", width = 10, height = 6)
plot(mybarplots2)
dev.off()
